Lessons Learned from Differential Testing JS Engines

### 2018-07-03 paper/paper.tex
pass on structure

\title{Should I Fuzz my Inputs or Improve my Test Suite? Lessons from
  Differential Testing Runtime Engines.}

@@

\begin{abstract}
Differential testing has shown to be a successful approach to finding
bugs in compilers and runtime engines. This paper assesses the impact
that the fuzzing strategy and the test suites have in bug-finging
ability. We focused on JavaScript and WebAssembly runtime
engines. \Fix{...}
\end{abstract}

@@

JavaScript (\js{}) is one of the most popular programming languages
for the web today~\cite{business-insider,stackify}. The interest of
the community in the JS ecossystem incentivizes improvements both in
the language and their runtime engine implementations. It is natural
to expect that such improvements will entail sensible changes in
engine implementations~\cite{kangax} that could lead to
errors. Finding bugs on JS engines is therefore and important
problem. Automated techniques, such as Fuzz Testing~\cite{fuzz-bart},
have shown successful at finding universal errors, such as memory
errors~\cite{libfuzzer-tutorial}. However, they don't address the
problem of finding functional errors that could arise when an engine
does not adhere to the specification.

This paper reports on a study to find those kinds of bugs in
JavaScript engines.\Mar{revise...a study answer questions? the
  statement is more propositive.} The goal of the study is to improve
quality of existing \js{} engines by improving the bug-finding
process. We used differential testing~\cite{Brumley-etal-ss07}, a
technique that has been applied in a variety of
contexts~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}
to address the oracle problem. Differential testing leverages the
diversity across system's implementations to detect anomalous
behavior. \Mar{this needs work$\rightarrow$} \Fix{but it has not been
  thoroughly explored to find functional bugs in JS engines. The
  closest work was done by Patra and Pradel~\cite{patra2016learning},
  where they evaluated their proposed language-agnostic fuzzer to find
  cross-browser HTML+JS discrepancies. This project aims at building
  and evaluating an infrastructure for differential testing of runtime
  engines, such as the JS engine or WebAssembly's. The sensible parts
  of the infrastructure are the checks of input validity (as to reduce
  waste/cost) and output correctness (as to reduce false positives).}

@@

Figure~\ref{fig:workflow} illustrates the workflow of the
infrastructure we used in this study. Boxes denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cyclic icons denote repetition--the leftmost cyclic icon
indicates that each file in the input list will be analyzed in
separate and the rightmost icon indicates that a single file will be
processed multiple times in fuzzing mode. The bug-finding process
takes on input JS files from regression test suites of various JS
engines. Table~\ref{tab:test-suites} shows the JS sources we mined
from online repositories of various open-source engines. Overall, we
found a total of almost 36,5K JS files.

\begin{table}[h]
  \centering
  \caption{\label{tab:test-suites}Test Suites\Fix{use path in the repo}}
  \begin{tabular}{ccc}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    Duktape & \href{https://github.com/svaarala/duktape}{GitHub} & 997 \\
    JerryJS & \href{https://github.com/jerryscript-project/jerryscript}{GitHub} & 1.803 \\
    JSI & \href{https://github.com/technosaurus/jsish}{GitHub} & 99 \\
    Tiny-js & \href{https://github.com/gfwilliams/tiny-js}{GitHub} & 44 \\
    Mozilla & \href{-}{-} & 32414 \\
    V8.test.benchmarks.data & \href{https://github.com/svaarala/duktape/tree/master/tests/ecmascript}{GitHub} & 64 \\
    WebKit.jstests.es6 & \href{https://github.com/svaarala/duktape/tree/master/tests/ecmascript}{GitHub} & 605 \\
    WebKit.jstests.microbenchmarks & \href{https://github.com/svaarala/duktape/tree/master/tests/ecmascript}{GitHub} & 426 \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. The HI
group includes those inputs where execution manifests anomaly in the
test code (or its close neighborhood) as opposed to some internal JS
function. The rationale is that the test in this group executed
without violating any internal checks of the API.
The LO group, in contrast, includes those cases where the anomaly
was observed executing some JS function. We found that engine
implementations often check pre-conditions of API functions
differently, leading to premature failures which manifest themselves as
discrepancy in our infrastructure. Although we did find real bugs from
warnings in the LO group, the proportion was much lower compared to the HI
group--only 12\% of the reals bugs we found originated from the LO
category. \Mar{show real examples of HI and LO and provide the
  rationale for such classification.} \Mar{can we detect dups mining
  issue trackers?}

@@

\section{Methodology}
\label{sec:methodology}

The goal of this study is to assess the impact of fuzzing in finding
bugs with differential testing. In this section, we discuss
the methodology applied to prepare our environment for the experiments.
The dependents and independents variables
will be discuss in Section~\ref{sec:results}.

\subsection{Engines.}~We used the following engines in
this study: Microsoft's Chakra~\cite{chakra2018repo}, Google's v8~\cite{v82018repo},
Mozilla's SpiderMonkey~\cite{spidermonkey2018repo}, and Apple's JavaScriptCore
(WebKit)~\cite{jsc2018repo}. We selected these engines based on
popularity~\Fix{cite}. Considering fuzzing tools, we used
representatives of the most popular approaches to fuzzing. For
random-based fuzzing we used Radamsa~\cite{radamsa}; for
coverage-based fuzzing we used
\Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
generative-based fuzzing we used
\Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
be found elsewhere~\cite{fuzz-bart}.

\subsection{Seeds.}~This section describes 
how we found valid javascript files based on 
existing sources on the open-source repositories.
Originally, we looking JS engines repositories that we 
support (ie. V8, SpiderMonkey, Chakra and JavascriptCore) getting
their regression suites and benchmarks testing involving javascript files.
In addition, we mined repositories from GitHub based on the following criteria:
\begin{itemize}
  \item The project must be an open-source project and at least 1K stars from community.
  \item The repository must have JavaScript tests included.
  \item The tests should be plug-and-play and/or easy integration.
\end{itemize}

We focused on JavaScript Engines for its capacity to testing the
interpreter with pure JS files. The Figure~\ref{fig:query} 
illustrates the query to the Github API as an HTTP request, the result 
is sorted in descending order of stars. Initially, we obtained
a total of \Fix{XX} projects. Manually, we follow the criteria to exclude 
invalid projects and we obtained a total of \Fix{XX} repositories.

\begin{figure}
  \centering
  \begin{lstlisting}
https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
  \end{lstlisting}
  \caption{\label{fig:query}
  Query to the GitHub API for JS engines projects that contains at least 1K of stars from community.\Fix{fix query}
  }
\end{figure}

Due the variance of engines implementations, many projects uses distinct frameworks for testing 
and require external libs to run their testing suites. We try to use only the JS file with minor fixes
to support our environment. These fixes are composed by an assertion function that throws an Error that
we can capture by our infraestruture. 
% For example to run the JerryScript tests it was necessary 
% use the unit-test package to run it, but with our changes we added the assertion
% does not have an assertion in the test file
% \Fix{add code to explain}

\subsection{Fuzzers}
Fuzzers grammar-based can generate a new file through a language grammar (ie. BNF).
Our infrastructure supports any grammar fuzzer with a few adjusts. However, 
we try to integrate several grammar-based fuzzers, for example 
Grammarinator~\footnote{https://github.com/renatahodovan/grammarinator}, QuickFuzz~\cite{grieco2016quickfuzz}
and \Fix{others fuzzers} to generate new JavaScript files based on grammar, but 
after several runs it was observed that this approach was ineffective
due the amount of invalid files and/or files without discrepancies. For example, if we ran 
Grammarinator to generate 1K JS files ten times with a random seed generation, we obtained
\Fix{XX\%} of valid files. Checking in our environment almost \Fix{XX\%}
are js files that shows undefined variables and due the differential testing in our environment
all engines will raise a SyntaxError and this approach was not relevant to our experiment.

>>>>

%Should I Fuzz my Inputs or Improve my Tests? 
\title{Lessons Learned from Differential Testing JS Engines}

@@

%% page numbering -M
\thispagestyle{plain}
\pagestyle{plain}

%% JavaScript (\js{}) is a popular programming language for the
%% web. Finding errors in JS runtime engines is an important problem.
\begin{abstract}
This paper assesses the impact of Differential Testing (DT) to find
functional bugs in JS engines. This is an important problem given the
importance of JS today. DT has shown successful in finding bugs in
compilers and runtimes, but has not been thoroughly explored in this
important domain. Our study \Fix{...}
\end{abstract}

@@

JavaScript (\js{}) is today one of the most popular programming
languages for the web~\cite{business-insider,stackify}. The interest
of the community for the language encourages constant improvements in
its specification and implementations. It is natural to expect that
such improvements will entail sensible changes in runtime
engines~\cite{kangax}; changes that could lead to errors. Finding bugs
on JS engines is an important problem. In this paper, we are
particularly interested in finding functional (non-crash) bugs.

Differential testing~\cite{Brumley-etal-ss07} (DT) is a popular
approach that has been applied in a variety of contexts to find
functional
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17}. DT
automates test generation in scenarios where multiple implementations
of a system exist. It leverages the diversity across system's
implementations to detect anomalous behavior. This paper reports the
results of a study we conducted to assess the impact of DT in finding
bugs on \js{} engines.

\Mar{this needs work$\rightarrow$} \Fix{but it has not been
  thoroughly explored to find functional bugs in JS engines. The
  closest work was done by Patra and Pradel~\cite{patra2016learning},
  where they evaluated their proposed language-agnostic fuzzer to find
  cross-browser HTML+JS discrepancies. This project aims at building
  and evaluating an infrastructure for differential testing of runtime
  engines, such as the JS engine or WebAssembly's. The sensible parts
  of the infrastructure are the checks of input validity (as to reduce
  waste/cost) and output correctness (as to reduce false positives).}

@@

Figure~\ref{fig:workflow} illustrates the workflow of the
infrastructure we used in this study. Boxes denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cycle icons denote repetition--the leftmost icon
indicates that each file in the input list will be analyzed in
separate whereas the rightmost icon indicates that a single file will be
processed multiple times in fuzzing mode. The bug-finding process
takes on input JS files from regression test suites of various JS
engines.

@@

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. The HI
group includes those inputs where execution manifests anomaly during
the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}. The rationale is that
the test in this group executed without violating any internal checks
of the API.  The LO group, in contrast, includes those cases where the
anomaly was observed during the execution of some API function. We
found that engine implementations often check pre-conditions of API
functions differently. It can happen, for example, that one engine
enforces a pre-condition that another engine does not. In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO and provide the rationale for such classification.}
\Mar{can we detect dups mining issue trackers?}

@@

\section{Objects of Study}
\label{sec:methodology}

This section discusses the objects we used in our study.

%% methodology we used in our study.  The
%% dependent and independent variables will be discuss in
%% Section~\ref{sec:results}.

\subsection{Engines}
\label{sec:methodology:engines}~We selected the most popular JS
engines on the web~\Fix{cite} to focus our bug-finding efforts, namely
Microsoft's Chakra~\cite{chakra2018repo}, Google's
v8~\cite{v82018repo}, Mozilla's
SpiderMonkey~\cite{spidermonkey2018repo}, and Apple's JavaScriptCore
(WebKit)~\cite{jsc2018repo}.

\subsection{Seed JS files}~We considered in our study test suites
associated with all four JS engines we analyzed
(section~\ref{sec:methodology:engines}). In addition, we mined test
suites from other repositories based on the following criteria:
\begin{itemize}
  \item The project must be an open-source project and at least 1K stars from community.
  \item The repository must have JavaScript tests included.
  \item The tests should be plug-and-play and/or easy
    integration.\Mar{not clear what you mean}
\end{itemize}

Figure~\ref{fig:query} illustrates the Github API query\Fix{cite} we
used.\Mar{identify sources assoc. with the four analyzed engines.} The results of this query is sorted in descending order of
stars. Initially, we obtained a total of \Fix{XX} projects. Manually,
we follow the criteria to exclude invalid projects and we obtained a
total of \Fix{XX} repositories. Table~\ref{tab:test-suites} shows the
JS sources we considered. Overall, we found a total of \totfiles{} JS
files.\Mar{Briefly explain these names}

\begin{table}[h]
  \centering
  \caption{\label{tab:test-suites}Test Suites}
  \begin{tabular}{ccr}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    Duktape & \cite{duktape} & 997 \\
    JerryJS & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\
    Mozilla & \Fix{??} & 32,414 \\
    V8.test.benchmarks.data & \Fix{??} & 64 \\
    WebKit.jstests.es6 & \Fix{??} & 605 \\
    WebKit.jstests.microbenchmarks & \Fix{??} & 426 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}

\begin{figure}
  \centering
  \begin{lstlisting}
https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
  \end{lstlisting}
  \caption{\label{fig:query}
  Query to the GitHub API for JS engines projects that contain over 1K stars.\Fix{fix query}
  }
\end{figure}

It is worth noting that many projects use distinct frameworks for
testing and require external libraries to run their testing
suites. For some projects, we made small changes in the testing
infrastructure to be able to uniformly run the test in all
engines.\Mar{not entirely clear what you did to support
  this.$\rightarrow$}We aimed to use only the JS file with minor fixes
to support our environment. These fixes are composed by an assertion
function that throws an Error that we can capture by our
infraestruture.

% For example to run the JerryScript tests it was necessary 
% use the unit-test package to run it, but with our changes we added the assertion
% does not have an assertion in the test file
% \Fix{add code to explain}

\subsection{Fuzzers}

\Mar{revise...}~We used representatives of popular fuzzing approaches. For
random-based fuzzing we used Radamsa~\cite{radamsa}; for
coverage-based fuzzing we used
\Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
generative-based fuzzing we used
\Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
be found elsewhere~\cite{fuzz-bart}.

Fuzzers grammar-based can generate a new file through a language grammar (ie. BNF).
Our infrastructure supports any grammar fuzzer with a few adjusts. However, 
we try to integrate several grammar-based fuzzers, for example 
Grammarinator~\footnote{https://github.com/renatahodovan/grammarinator}, QuickFuzz~\cite{grieco2016quickfuzz}
and \Fix{others fuzzers} to generate new JavaScript files based on grammar, but 
after several runs it was observed that this approach was ineffective
due the amount of invalid files and/or files without discrepancies. For example, if we ran 
Grammarinator to generate 1K JS files ten times with a random seed generation, we obtained
\Fix{XX\%} of valid files. Checking in our environment almost \Fix{XX\%}
are js files that shows undefined variables and due the differential testing in our environment
all engines will raise a SyntaxError and this approach was not relevant to our experiment.
